### 2024-03-21 doc/15yrsChange.Rmd
adding data objects to the rmarkdown

#low canopy vulnerability
ldlv_ABG_2018 <-  figure2_agb  %>% filter(Year == "2018" & Group == "1")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
ldlv_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "1")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
hdlv_ABG_2018 <-  figure2_agb  %>% filter(Year == "2018" & Group == "2")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1) 
hdlv_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "2")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)

>>>>

#high deer, low canopy vulnerability
hdlv_AGB_2013 <- figure2_agb %>% filter(Year == "2013" & Group == "2") %>% pull(Abg_C_Mg_Ha) %>%
round(digits = 1)
hdlv_AGB_2018 <- figure2_agb %>% filter(Year == "2018" & Group == "2") %>% pull(Abg_C_Mg_Ha) %>%
round(digits = 1)
hdlv_AGB_2023 <- figure2_agb %>% filter(Year == "2023" & Group == "2") %>% pull(Abg_C_Mg_Ha) %>%
round(digits = 1)

#low deer, low canopy vulnerability
ldlv_ABG_2018 <-  figure2_agb  %>% filter(Year == "2018" & Group == "1")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
ldlv_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "1")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)
hdlv_ABG_2018 <-  figure2_agb  %>% filter(Year == "2018" & Group == "2")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1) 
hdlv_ABG_2023 <- figure2_agb  %>% filter(Year == "2023" & Group == "2")  %>%  pull(Abg_C_Mg_Ha)  %>% round(digits = 1)

##Figure 3

#Net Biomass Change 
#Group 1
nbc_group1_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "1" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_group1_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "1" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_group1_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "1" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 2
nbc_group2_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "2" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_group2_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "2" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_group2_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "2" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 3 
nbc_group3_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "3" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_group3_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "3" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_group3_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "3" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Whole Plot
nbc_wholePlot_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "Whole Plot" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_wholePlot_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "Whole Plot" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
nbc_wholePlot_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "Whole Plot" & Flux == "NetFlux") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Aboveground Woody Growth 
#Group 1
awg_group1_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "1" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_group1_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "1" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_group1_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "1" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 2
awg_group2_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "2" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_group2_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "2" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_group2_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "2" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 3
awg_group3_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "3" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_group3_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "3" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_group3_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "3" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Whole Plot
awg_wholePlot_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "Whole Plot" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_wholePlot_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "Whole Plot" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awg_wholePlot_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "Whole Plot" & Flux == "AWP") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Aboveground Woody Mortality 
#Group 1
awm_group1_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "1" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_group1_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "1" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_group1_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "1" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 2
awm_group2_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "2" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_group2_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "2" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_group2_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "2" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 3
awm_group3_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "3" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_group3_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "3" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_group3_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "3" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Whole Plot
awm_wholePlot_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "Whole Plot" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_wholePlot_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "Whole Plot" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awm_wholePlot_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "Whole Plot" & Flux == "AWM") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Aboveground Woody Recruitment
#Group 1
awr_group1_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "1" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_group1_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "1" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_group1_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "1" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 2
awr_group2_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "2" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_group2_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "2" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_group2_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "2" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Group 3
awr_group3_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "3" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_group3_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "3" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_group3_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "3" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

#Whole Plot
awr_wholePlot_2013 <- fig3_woodyfluxes %>% filter(Census == "2" & Group == "Whole Plot" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_wholePlot_2018 <- fig3_woodyfluxes %>% filter(Census == "3" & Group == "Whole Plot" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)
awr_wholePlot_2023 <- fig3_woodyfluxes %>% filter(Census == "4" & Group == "3" & Flux == "AWR") %>% pull(MgC_Yr_Ha) %>% round(digits = 1)

##Figure 4

#Averages

#5 Year Averages for top three species

#Peak for each species
```
